An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-16 VLDB2026/main.tex
Update main.tex

	Most algorithms exhibit the worst performance on the OOD dataset text2image. However, ACORN, UNG, and FilteredVamana show relatively stable performance on text2image. Their performance drops less compared to in-distribution (ID) datasets such as GIST and GLOVE, indicating better adaptability to OOD queries.

>>>>

	Most algorithms exhibit the worst performance on the OOD dataset Text2Image. However, ACORN, UNG, and FilteredVamana show relatively stable performance on Text2Image. Their performance drops less compared to in-distribution (ID) datasets such as GIST1M and GloVe, indicating better adaptability to OOD queries.
